### 2025-02-22 paper/sections/ExperimentalSetup.tex
add results

This section describes the experimental setup, providing details about data splits, preprocessing steps, hyperparameter tuning, and the tools and libraries utilized. The goal is to ensure reproducibility, transparency, and alignment with established best practices in machine learning research.

\subsection{Data Splits and Usage}

The dataset was divided into three subsets: training, development (validation), and testing. Specifically, 80\% of the training dataset was allocated for training, while the remaining 20\% was reserved for validation to facilitate model selection. Once the best-performing model was identified during the validation phase, the entire training and development datasets were combined to retrain the final model. This final model was then evaluated on the test dataset, which was held out during the entire training process to ensure an unbiased assessment of the model's generalization performance. This approach adheres to standard practices in machine learning research to prevent data leakage and ensure robust evaluation \citep{Goodfellow-et-al-2016}.

@@

>>>>

This section describes the experimental setup, providing details about data splits, preprocessing steps, hyperparameter tuning, computational resources, and the tools and libraries utilized. The goal is to ensure reproducibility, transparency, and alignment with established best practices in machine learning research.
\input{tables/MainResults}

\subsection{Data Splits and Usage}
%TODO: refer to dataset used
The dataset was divided into three subsets: training, development (validation), and testing. Specifically, 80\% of the training dataset was allocated for training, while the remaining 20\% was reserved for validation to facilitate model selection. Once the best-performing model was identified during the validation phase, the entire training and development datasets were combined to retrain the final model. This final model was then evaluated on the test dataset, which was held out during the entire training process to ensure an unbiased assessment of the model's generalization performance. This approach adheres to standard practices in machine learning research to prevent data leakage and ensure robust evaluation \citep{Goodfellow-et-al-2016}.

@@

\subsection{Computational Resources}

All experiments were run on a Kaggle Tesla P100 GPU, which provided the necessary computational power to efficiently train and evaluate the models. The use of a Tesla P100 allowed for accelerated processing, making it feasible to leverage complex models and extensive hyperparameter tuning within a reasonable timeframe. This setup ensures that the experiments are reproducible and can be replicated by other researchers with access to similar hardware.

### 2025-02-22 paper/sections/SystemOverview.tex
add results

The preprocessing pipeline involves multiple steps to clean and standardize the text data. Initially, all text is converted to lowercase and unnecessary whitespace is removed. Then, special characters, URLs, and emojis are filtered out using regular expressions. Each emoji is replaced by its corresponding title (e.g., \smiley → "smiling face"). Tokenization is performed using language-specific tokenizers to ensure optimal segmentation. Finally, stopwords are removed, and text normalization techniques, such as stemming or lemmatization, are applied where appropriate.

@@

>>>>

The preprocessing pipeline involves multiple steps to clean and standardize the text data. Initially, all text is converted to lowercase, and unnecessary whitespace is removed. Special characters, URLs, and emojis are filtered out using regular expressions. Emojis, in particular, are replaced with their corresponding textual descriptions (e.g., \smiley $\rightarrow$ ``smiling face''). Tokenization is performed using language-specific tokenizers to ensure optimal segmentation. Finally, stopwords are removed, and text normalization techniques, such as stemming or lemmatization, are applied where appropriate.

@@

For languages with sufficient pretrained models available, we identified the best-performing embedding model and paired it with SVM as the classifier. This approach leverages the strengths of the pretrained embedding models in capturing language-specific nuances, while the SVM classifier ensures robust performance for multi-label classification. On the other hand, for languages with limited pretrained resources, we utilized the multilingual embedding model ``Multilingual-E5-large-instruct'' \citep{wang2024multilingual} in combination with XGBoost as the classifier. The ``Multilingual-E5-large-instruct'' model, designed to generalize across diverse languages, enabled the system to maintain high performance even in resource-constrained settings.

\subsection{Summary of Model Variants}
